\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=1in]{geometry}
\usepackage[parfill]{parskip}
\usepackage{array}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    citecolor={blue},
    urlcolor=blue
}

\begin{document}

% Title page for document
\begin{titlepage}
    \begin{center}
        \vspace*{1in}

        \Huge
        \textbf{Printing Money - Final Report}

        \vspace{0.25in}
        \LARGE
        A study on financial gain with 3D printing

        \vspace{1 in}

        \textbf{Tyler Conley}

        \vspace{0.5in}
        2023-04-26

        %%%
        %
        % Add Job Performed Table Here
        %
        %%%

        \vfill
    \end{center}
\end{titlepage}


\begin{center}
    \LARGE
    \textbf{Executive Summary}
\end{center}

Provide an executive summary, which should contain everything an executive summary should.

This section should include a discussion of 1) how the project adds to the understanding of the
area investigated; 2) the technical effectiveness and/or economic feasibility of the methods or
techniques investigated or demonstrated; and 3) how the project is otherwise of benefit to the
public. The discussion should be written in terms understandable by an educated layman

\begin{center}
    \LARGE
    \textbf{Acknowledgements}
\end{center}

\begin{center}
    \LARGE
    \textbf{Accomplishments and Objectives}
\end{center}

Provide a comparison of the actual accomplishments with the technical milestones and deliverables
of the project.

This award allowed John Doe Enterprise to demonstrate a number of key objectives. The focus
of the project was on building a Transformational \& Disruptive Technology.

A number of tasks and milestones were laid out at the beginning of the project. The actual
performance against the stated milestones is summarized here:

\begin{center}
    \begin{tabular}{| p{1.25in} | p{5.25in} |}
        \hline
        Tasks & Milestones and Deliverables \\
        \hline
        Task 1: Task title \newline 1.1 Subtask \newline 1.2 Subtask \newline 1.3 Subtask & Q1. Milestone as stated in statement of project objectives. \newline
        Actual Performance: (Completion date) Performer states progress against the milestone and completion date. Should be as quantitative as possible \newline
        Q2: Milestone as stated in statement of project objectives \newline Actual Performance: (Completion Date) Performer states progress against the milestone
        and completion date. Should be as quantitative as possible \\
        \hline
    \end{tabular}
\end{center}

For projects involving computer modeling, provide a brief description of the model, key assumptions, how the model was validated, and whether or not the
model and results were presented in peer-reviewed publications.

\begin{center}
    \LARGE
    \textbf{Project Activities}
\end{center}

One paragraph that succinctly summarizes the project's focus, major approaches and hypotheses utilized, and a high-level summary of the project's results.

If there was a modification to the award as a result of changes in tasks or milestones, state when that occurred and provide a brief narrative describing the change.

\begin{center}
    \LARGE
    \textbf{Project Activities}
\end{center}

\begin{enumerate}
    \item \textbf{Description of Code}
        Can reference a good README, should be enough to run the code.
    \item \textbf{Expected Outcomes of Running Code}
    \item \textbf{Results}
    \item \textbf{Other Products (e.g. Databases, Physical Collections, Audio/Video, Software, Models, Educational Aids or Curricla, Equipment or Instruments)}
\end{enumerate}

\end{document}
